Smart concentrated liquidity

### 2022-12-21 Uniswapv3concentratedliquidity/main.tex
og

\section{Building different flavours :market-neutral, long, short}
Simply bringing liquidity in a uniswap v3 position is a risky strategy. In addition to a nasty v3 impermanent loss, you can also incur the depreciation of the long side of the LP position in case of a negative price action for the risky asset.\\
To avoid this double penalty, one has to devise ways to take directional positions (both long and short) and take directional bets to benefit from bearish market stages too.\\
Or simply become market neutral by removing 
\subsection{Neutral leg}
\subsubsection{Configuration}
    \includegraphics[scale=0.07]{Plots/neutral_leg.png}
    \caption{Neutral}
    \label{fig:neutral_leg}
The neutral configuration is achieved by using a money market to borrow the risky asset. We enter with a non risky/stable asset and borrow the risky part of the LP position through the money market. This has a cost incurred because of the borrowing on the money market.\\
We enter with an amount $U$ of stable asset.\\
The splitting quantities $\omega_1$ and $\omega_2$ must verify : 

@@

\begin{array}{ll}
\omega_1 + \omega_2 = 1\\https://www.overleaf.com/project/63982f2b00b8e4f60c47ea82
\omega_1 * U = X_{risky}*\omega_2 * U\\    

@@

, where $X_{risky}$ is the risky collateral ratio : the amount of risky asset you can borrow against your stable asset.\\
The solution is given by the splitting quantities :

@@

\left\{
\begin{array}{ll}
\omega_1  = \frac{X_{risky}}{1+X_{risky}}\\
\omega_2  = \frac{1}{1+X_{risky}}\\
\end{array}\right.

@@

\subsubsection{Operation}
To avoid the risk of being liquidated, we will only borrow $X << X_{risky}$ leading to a clearly smaller LP position when compared to the entry size. This will lead to lower yield but a safer strategy.\\
Impermanent loss can be nasty, and we want to have a safe buffer to avoid liquidation.\\
Now that the asset has been borrowed, our position is only subject to the impermanent loss.\\
\subsection{Long/Short legs}
\subsubsection{Long leg}
    \includegraphics[scale=0.035]{Plots/long_leg.png}
    \caption{Long}
    \label{fig:long_leg}
The splitting quantities $\omega_1$ and $\omega_2$ must verify : 

@@

\begin{array}{ll}
\omega_1 + \omega_2 = 1\\
\omega_1 * A = X_1*\omega_2 * A\\    

@@

, where $X_1$ is the collateral ratio : the amount of stable coins you can borrow against your Solana.\\
The solution is given by the splitting quantities :

@@

\left\{
\begin{array}{ll}
\omega_1  = \frac{X_1}{1+X_1}\\
\omega_2  = \frac{1}{1+X_1}\\
\end{array}\right.

@@

\subsubsection{Short leg}
    \includegraphics[scale=0.035]{Plots/short_leg.png}
    \caption{Short}
    \label{fig:short_leg}
The splitting quantities $\omega_1$ and $\omega_2$ must verify : 

@@

\begin{array}{ll}
\omega_1 + \omega_2 = 1\\
\omega_1*U = (1-x)*\omega_2*X_2*U\\    

@@

, where $X_2$ is the collateral ratio : the amount of sols you can borrow against your stable coin and $x$ is the proportion of your borrowed Sols you use to short.\\
The solution is given by fixing the amount you have to short as a function of your liquidity position size $\omega_1$ ($x=f(\omega_1)$):

@@

x = \frac{(1-\omega_1)*X2-\omega_1}{(1-\omega_1)*X2}

@@

So according to the risk level from our proprietary indicator for the next epoch, we can taylor the $\frac{short}{long}$ position ratio in a continuous way by allocating specific sizes of risky and numeraire asset:\\
\begin{equation}
\left\{
\begin{array}{lll}
\frac{A}{U} = \left((1-\omega_1)*X2-\omega_1 \right)\text{market neutral} \\
\frac{A}{U} > \left((1-\omega_1)*X2-\omega_1 \right) \text{long overall} \\
\frac{A}{U} < \left((1-\omega_1)*X2-\omega_1 \right)\text{short overall}  \\
\end{array}
\end{equation}
\section{Actively rebalancing your liquidity for a market neutral solution}
Let us here consider the market neutral configuration : we have entered an LP position with a borrowed risky asset and are therefore only subject to the impermanent loss.\\
As demonstrated in the appendix \ref{v3isbad}, V3 impermanent loss can be nasty, and the tighter you encompass your price, the more violent it becomes.\\
We here under propose a quantitative algorithm to dynamically mitigate it.\\
\subsection{Dynamical exiting}
Market making is in essence a very complex topic. Professional traditional finance market makers have advanced algorithmic trading to manage their risk and avoid market trends.\\
Market makers profit only from rangy markets and must exit as soon as a trend takes hold (upward and downward).\\
V3 liquidity provisioning is market making in essence and V3 concentrated liquidity ressembles an order book.\\

\subsubsection{Trend exiting signal}
Based on a proprietarly hourly volatilitity/trend detecting signal, we manage to capture trendy versus rangy market hours.\\
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{Plots/signal_hourly.png}
    \caption{On/Off Liquidity provisionning signal}
    \label{fig:signal_hourly}
\end{figure}
This signal exhibits a very strong correlation to the hourly price return (60\% over 5 years).\\
The idea is to use an epsilon threshold to trigger an exit signal to discriminate the hours where we will enter liquidity and the ones where we won't (methodology described in figure \ref{fig:signal_hourly}).\\
We here display the reconstituted performance of a strategy which would be long when we will provide liquidity provision (for a signal such that $\abs(S_t)<\epsilon$) for different epsilons :
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/signal_ETH.png}
    \caption{Rangy market capture}
    \label{fig:signal_hourly}
\end{figure}
We see the signal is making a good job at capturing rangy market.\\
\section{Modelling generated fees}
\subsection{Dex volume historical data}
We fetch the specific ETH-USDC volume on Uniswap V3 for the 0.3\% fee pool using the graph protocol.
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/dex_volume_ETH.png}
    \caption{Rangy market capture}
    \label{fig:dex_volume}
\end{figure}
\subsection{Generated fees and v3 bounds}
We take a snapshot of the APY generated by a LP position whose bounds have been placed around $x\%$ for $x$ varying between 1\% to 300\%.
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/apy_snapshot_ETH.png}
    \caption{Rangy market capture}
    \label{fig:apy_snapshot}
\end{figure}

\subsection{Generated fees historical data}
We then model the generated fees by a simple rule thumb of pro rata dex volume to get historical data.
\begin{equation}
APY\left(t\right) = APY\left(T\right) * \frac{DEX-VOLUME\left(t\right)}{DEX-VOLUME\left(T\right)}
\end{equation}
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/apy_over_time_ETH.png}
    \caption{APY over time as a function of the v3 bound tighteness}
    \label{fig:apy_over_time}
\end{figure}
This is a necessary approximation as we can't reproduce the whole past liquidity profile.\\

\begin{description}
  \item[$\bullet$ Daily Fees = Pool Volume * Pool Fee \% * Liquidity Coverage Expected Value]
  \item[$\bullet$ APY = (Daily Fees / 1000) * 365\\]
\end{description}
Finally choose the highest APY position for each pool
\subsection{Encompassing the market by defining bounds}
The idea behind Uniswap V3 is that the user can and must specify a price range where he wants to bring the liquidity for a better capital efficiency.
\\
It also means that the procedure is not as straightforward as in Uniswap V2 and requires retail liquidity provider to have at least an opinion on the optimal bounds to choose.\\
The price range is specified by two bounds on the risky asset price $P_a <= P_b$ and the liquidity brought by the user will only account for that range allowing a huge gain in capital efficiency.\\
The tighter the bounds, the more efficient the liquidity capital is, but the more you will have to rebalance and incur impermanent loss and swapping costs.\\

The bounds are fixed by a $x\%$ distance around the initial position entering $P_0$ price.
\begin{equation}
P_b = P_0 + x*P_0
\end{equation}
\begin{equation}
P_a = P_0 - x*P_0
\end{equation}
\begin{equation}
P_0 = \frac{P_a + P_b}{2} 
\end{equation}
Getting an idea of the proper optimal $x$ is the topic of the next sections. 
\subsection{IL incurred at liquidity exit triggered}
If we were to rebalance each time a bound is reached, we can rewrite the v3 impermanent loss according to the strategy. \\
By noting $\kappa = \frac{P_b}{P_a} = \frac{P_0 + x*P_0}{P_0-x*P_0}  $, the v3 impermanent loss can be rewritten:
\begin{equation}\label{eq:ILv3Stratbis}
\frac{V_{arbitraged} - V_{held}}{V_{held}} = 
IL_{v2}(\tau)*\frac{1}{1 -\frac{ \sqrt{\frac{2}{1 +\kappa}} + \tau*\sqrt{\frac{1}{2}(1+\frac{1}{\kappa})}} { 1+\tau}}}
\end{equation}
where $\tau = \frac{P_t}{P_0}$ as defined in the appendix \ref{eq:deftau}.
Maximum incurred impermanent loss will happen if a position is exited when one of its bound is reached. Two different maximum incurred IL loss depending on whether we reached the lower bound or the upper bound.\\
Upper bound reached impermanent loss:\\
\begin{equation}
\tau_{up} = \frac{P_0+x*P_0}{P_0} > 1   
\end{equation}
Lower bound reached impermanent loss:\\
\begin{equation}
\tau_{down} = \frac{P_0-x*P_0}{P_0} < 1   
\end{equation}
Equation \ref{eq:ILv3Stratbis} and its simplified version \ref{nasty_il} shows how nasty v3 impermanent loss can be for tighter bounds.\\
But this configuration will rarely be hit, as the volatily exiting signal will most likely prevent trendy market which would lead to that case.\\
Most of the time, $P_t \approx P_0 $ resulting in a $IL \approx 0$.\\
That is the whole goal of the exiting signal.\\
\subsection{No swapping cost for the market neutral}
For huge AUM (asset under management) and fully on-chain rebalancing vaults, price slippages occurring during swaps can be very detrimental to the strategy.\\
The market neutral version has a huge advantage : no swapping will be required.\\
The asset is borrowed and liquidity will only be added/removed liquidity according to our signal.\\
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.25]{Plots/lp_over_time.png}
    \caption{APY over time as a function of the v3 bound tighteness}
    \label{fig:apy_over_time}
\end{figure}

\section{Exhaustive optimization}
\subsection{Getting the optimal parameters: A trade-off between IL, transaction costs and generated LP fees}
Optimal bound distance $x$, volatility exiting signal $\epsilon$ must be calibrated for an optimal APY.
\\
\begin{description}
\item[$\bullet$]Maximize price inside the tightest bounds to earn most LP fees (the tighter the bounds, the efficienter the capital)
\item[$\bullet$]Calibrate liquidity provision signal epsilon : a small epsilon will bring very low impermanent loss but also very low LP fees as your market making time proportion will drastically drop.   \item[$\bullet$] Add/remove transaction costs have to be minimized
\end{description}
We here propose an exhaustive search of the optimal parameters by running a backtest for each configuration and choosing the solution with the best Sharpe ratio.\\
\begin{equation}
\max_{(x, epsilon)} \left[ Sharpe\left(x, epsilon\right)\right]
\end{equation}
where $Sharpe\left(x, epsilon\right)$ is the sharpe ratio of the backtested path with $x$ and $epsilon$ as specific parameters for the algorithm.

\section{Results}\label{result}
The optimal parameters chosen after an exhaustive search are :
\begin{equation}
\left\{\begin{array}{lll}
early-exit = True\\
x = 3\%\\
\epsilon = 80\%
\end{array}
\right.
\end{equation}
\subsection{Absolute performance}
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/PL_generated_fees_against_IL_borrow rate_transaction cost_ETH.png}
    \caption{Absolute performance}
    \label{fig:abs_perf}
\end{figure}
We here plot the absolute performance of the strategy in stable coin. \\
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/Generated_fees_against_IL_ETH.png}
    \caption{Compounded generated liquidity fees versus IL v3 loss}
    \label{fig:fees_agains_apr}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/IL_v2_v3_ETH.png}
    \caption{Compounded generated liquidity fees versus IL v3 loss}
    \label{fig:il_v2_v3}
\end{figure}

\section{Hedging the position}
The \ref{result} results section clearly expose that the biggest losses for that strategy in absolute performance are when the risky underlying price drops. If it drops enough to trigger a rebalancing, then we have a concurrence of impermanent loss, risky asset depreciation and swapping costs which can ruin multiple months of fees generation.\\
We therefore here propose to modulate the strategy by using proprietary trend following forecasting indicator to give a downside risk level for the epoch to come.\\
According to that indicator, we here under propose two different methodologies.

\section{Conclusion}
https://medium.com/@RoboVault/delta-neutral-strategy-deep-dive-ae91d309b504
https://arxiv.org/abs/2208.03318
https://arxiv.org/pdf/2106.14404.pdf
https://uniswapv3.flipsidecrypto.com/
https://uniswaptimizer.com/
https://app.flipsidecrypto.com/velocity/queries/efed0457-5edc-46fa-ad7b-cffd01d5b93d
https://app.flipsidecrypto.com/velocity/queries/bb47119b-a9ad-4c59-ac4d-be8c880786e9
https://arxiv.org/pdf/2106.12033.pdf
https://medium.com/auditless/impermanent-loss-in-uniswap-v3-6c7161d3b445 
\appendix
\section{Understanding the risk of hyperbolic dexes (decentralized exchanges)}
\subsection{Hyperbolic equation}
Let $X$ denote the reserve of the risky asset (Ether, WBtc, SOL) and $Y$
denote the reserve of the non risky stable coin (USDT, USDC, BUSD, ..).
Uniswap pioneering approach was to force the reserve quantities on the pool to live on an hyperbole, hence the denomination hyperbolic dex.
\begin{equation}
    X * Y = cte = X_{t0} * Y_{t0}
\end{equation}
The constant is fixed by the initially brought amount at instant $t0$.
The risky asset price $X$ in stable coins $Y$ is directly linked to the pool reserve:
\begin{equation}
    P_{X \text{ in }Y}  = \frac{Y}{X} = P_X
\end{equation}
Basically if you have one Ether (X = 1) and 4500 USDT in the pool (Y = 4500), the ether
price is $\frac{4500}{1}$. And vice versa
\begin{equation}
    P_{Y \text{ in }X}  = \frac{X}{Y} = P_Y
\end{equation}
By denoting $L^2 = X_{t0} * Y_{t0}$ (L can be seen as the part of the liquidity brought by a single asset of the pool), a quick computation gives:
\begin{equation}
    L=\sqrt{X*Y}
\end{equation}
\begin{equation}
    X = \frac{L}{\sqrt{P_X}}  
\end{equation}
\begin{equation}
    Y = L*\sqrt{P_X}
\end{equation}

@@

Let's define $P_{consensus}$, the new price coming from a market consensus and $\tau>0$ the price ratio.
\begin{equation}\label{eq:deftau}
P_{consensus} = \tau*P\\
\end{equation}

@@

Finally, setting $\tau$ to 1, we do get 0 since there should not be any impermanent loss in any scenario, v2 or v3.\\
\subsubsection{V3 Impermanent loss is larger}\label{v3isbad}
If we take the simple assumption $p_a = \frac{P}{n}$ and $p_b = n*P$, we get the following loss :
\begin{equation}\label{nasty_il}
IL_{P_a,P_b}(\tau) = IL(\tau) * \frac{1}{1-\frac{1}{\sqrt{n}}}
\end{equation}
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/factor.png}
    \caption{Impermanent loss V3 factor}
    \label{fig:rangy_market}
\end{figure}

Even if our liquidity range is big enough to accommodate prices doubling or halving, impermanent loss is nearly 4 times higher than if we provided liquidity in the whole range of prices.\\
And that is excluding the impermanent loss associated with falling outside the concentrated liquidity range.\\
\subsection{Uniswap V3 LP liquidity providing value}
\subsubsection{Add/deletion of liquidity}
When adding or removing liquidity from a position, the amount of assets to add according to the amount of added liquidity $\Delta L$
is given by the equivalent formula as \ref{three_regime}:
\begin{equation}\label{liquidity_adding}
\left\{
\begin{array}{cc}
\begin{array}{lllll}
\left\{
\begin{array}{ll}
\Delta X=0\\
\Delta Y=\Delta L*(\sqrt{P_b}-\sqrt{P_a})\\
\end{array}
\right. & ,P\ge P_b\\
& \\
\left\{
\begin{array}{ll}
\Delta X=\Delta L*(\frac{1}{\sqrt{P}}-\frac{1}{\sqrt{P_b}}) \\
\Delta Y= \Delta L*(\sqrt{P}-\sqrt{P_a})\\
\end{array}
\right.&  ,P_a \le P \le P_b \\
&\\
\left\{
\begin{array}{ll}
\Delta X=\Delta L*(\frac{1}{\sqrt{P_a}}-\frac{1}{\sqrt{P_b}})\\
\Delta Y=0\\
\end{array}
\right.& ,P\le P_a\\
\end{array}
\right.\\
\end{array}
\end{equation}
\subsubsection{Valuing a liquidity position}
The initial amount of tokens $X_0$, $Y_0$ and $L$ when entering a LP position with bounds $P_a$ and $P_b$ and initial price $P_0$ will follow \ref{three_regime}.\\
You can deduct $L$ value from \ref{three_regime} applied to $X_0$, $Y_0$ and $P_0$.\\
The final amount of tokens $X$, $Y$ and $L$ when exiting a LP position with bounds $P_a$ and $P_b$ and current price $P$ will also follow \ref{three_regime} for the previous $L$.\\
The liquidity position P&L can be written as :
\begin{equation}\label{PnL}
PnL = \frac{X* P + Y}{X_0 * P_0 + Y_0} - 1
\end{equation}
\bibliographystyle{IEEEtranN}
\bibliography{bib}
\nocite{*}
\end{document}

>>>>

\section{Understanding the risk of hyperbolic dexes (decentralized exchanges)}
\subsection{Hyperbolic equation}
Let $X$ denote the reserve of the risky asset (Ether, WBtc, SOL) and $Y$
denote the reserve of the non risky stable coin (USDT, USDC, BUSD, ..).
Uniswap pioneering approach was to force the reserve quantities on the pool to live on an hyperbole, hence the denomination hyperbolic dex.

@@

    X * Y = cte = X_{t0} * Y_{t0}

@@

The constant is fixed by the initially brought amount at instant $t0$.
The risky asset price $X$ in stable coins $Y$ is directly linked to the pool reserve:

@@

    P_{X \text{ in }Y}  = \frac{Y}{X} = P_X

@@

Basically if you have one Ether (X = 1) and 4500 USDT in the pool (Y = 4500), the ether
price is $\frac{4500}{1}$. And vice versa

@@

    P_{Y \text{ in }X}  = \frac{X}{Y} = P_Y

@@

By denoting $L^2 = X_{t0} * Y_{t0}$ (L can be seen as the part of the liquidity brought by a single asset of the pool), a quick computation gives:

@@

    L=\sqrt{X*Y}

@@

@@

    X = \frac{L}{\sqrt{P_X}}  

@@

@@

    Y = L*\sqrt{P_X}

@@

@@

Let's define $P_{consensus}$, the new price coming from a market consensus and $\tau>0$ the price ratio.
\begin{equation}
P_{consensus} = \tau*P\\
\end{equation}

@@

Finally, setting $\tau$ to 1, we do get 0 since there should not be any impermanent loss in any scenario, v2 or v3.\\
\subsubsection{V3 Impermanent loss is larger}

If we take the simple assumption $p_a = \frac{P}{n}$ and $p_b = n*P$, we get the following loss :
\begin{equation}\label{nasty_il}
IL_{P_a,P_b}(\tau) = IL(\tau) * \frac{1}{1-\frac{1}{\sqrt{n}}}
\end{equation}
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.15]{Plots/factor.png}
    \caption{Impermanent loss V3 factor}
    \label{fig:rangy_market}
\end{figure}

Even if our liquidity range is big enough to accommodate prices doubling or halving, impermanent loss is nearly 4 times higher than if we provided liquidity in the whole range of prices.\\
And that is excluding the impermanent loss associated with falling outside the concentrated liquidity range.\\
\subsection{Uniswap V3 LP liquidity providing value}
\subsubsection{Add/deletion of liquidity}
When adding or removing liquidity from a position, the amount of assets to add according to the amount of added liquidity $\Delta L$
is given by the equivalent formula as \ref{three_regime}:
\begin{equation}\label{liquidity_adding}
\left\{
\begin{array}{cc}
\begin{array}{lllll}
\left\{
\begin{array}{ll}
\Delta X=0\\
\Delta Y=\Delta L*(\sqrt{P_b}-\sqrt{P_a})\\
\end{array}
\right. & ,P\ge P_b\\
& \\
\left\{
\begin{array}{ll}
\Delta X=\Delta L*(\frac{1}{\sqrt{P}}-\frac{1}{\sqrt{P_b}}) \\
\Delta Y= \Delta L*(\sqrt{P}-\sqrt{P_a})\\
\end{array}
\right.&  ,P_a \le P \le P_b \\
&\\
\left\{
\begin{array}{ll}
\Delta X=\Delta L*(\frac{1}{\sqrt{P_a}}-\frac{1}{\sqrt{P_b}})\\
\Delta Y=0\\
\end{array}
\right.& ,P\le P_a\\
\end{array}
\right.\\
\end{array}
\end{equation}
\subsubsection{Valuing a liquidity position}
The initial amount of tokens $X_0$, $Y_0$ and $L$ when entering a LP position with bounds $P_a$ and $P_b$ and initial price $P_0$ will follow \ref{three_regime}.\\
You can deduct $L$ value from \ref{three_regime} applied to $X_0$, $Y_0$ and $P_0$.\\
The final amount of tokens $X$, $Y$ and $L$ when exiting a LP position with bounds $P_a$ and $P_b$ and current price $P$ will also follow \ref{three_regime} for the previous $L$.\\
The liquidity position P&L can be written as :
\begin{equation}\label{PnL}
PnL = \frac{X* P + Y}{X_0 * P_0 + Y_0} - 1
\end{equation}

\section{Actively monitoring your liquidity}
\subsection{Encompassing the market by defining bounds from the Bollinger Bands}
The idea behind Uniswap V3 is that the user can specify a price range where he wants to bring the liquidity.
\\
The price range is specified by two bounds on the risky asset price $P_a <= P_b$ and the liquidity brought by the user will only account for that range allowing a huge gain in capital efficiency.\\
The tighter the bounds, the more efficient the liquidity capital is, but the more you will have to rebalance and incur impermanent loss and swapping costs.\\
Bollinger Bands are a type of price envelopes plotted at a standard deviation level above and below a simple moving average of the price. Because the distance of the bands is based on standard deviation, they adjust to volatility swings in the underlying price.\\
Bollinger Bands use 2 parameters, the 'Period' parameter T for the moving average and n or the number of standard deviations $\sigma$. \\
Bollinger bands help determine whether prices are high or low on a relative basis. They are used in pairs, both upper and lower bands and in conjunction with a moving average. Further, the pair of bands is not intended to be used on its own. Use the pair to confirm signals given with other indicators.\\
We will use Bollinger bands to define our liquidity price bounds at a specific rebalancing time $t$. The larger the number of standard deviations $n$, the broader the bands will get allowing a conservative liquidity range.\\
The bounds are fixed by the calibrated Bollinger band and the initial position entering $P_0$ price.
\begin{equation}
P_b = P_0 + n*\sigma
\end{equation}
\begin{equation}
P_a = P_0 - n*\sigma
\end{equation}
\begin{equation}
P_0 = \frac{P_a + P_b}{2} 
\end{equation}

\subsection{Rebalancing trigger}
If we were to rebalance each time a bound is reached, we can rewrite the v3 impermanent loss according to the strategy. \\
By noting $\kappa = \frac{P_b}{P_a} = \frac{P_0 + n*\sigma}{P_0-n*\sigma}  $, the v3 impermanent loss can be rewritten:
\begin{equation}\label{eq:ILv3Stratbis}
\frac{V_{arbitraged} - V_{held}}{V_{held}} = 
IL_{v2}(\tau)*\frac{1}{1 -\frac{ \sqrt{\frac{2}{1 +\kappa}} + \tau*\sqrt{\frac{1}{2}(1+\frac{1}{\kappa})}} { 1+\tau}}}
\end{equation}
A position is exited when one of its bound is touched, meaning that we will incur
two different IL loss depending on whether we reached the lower bound or the upper bound :
\begin{equation}
\tau_{up} = \frac{P_0}{P_0+n*\sigma}    
\end{equation}
\begin{equation}
\tau_{down} = \frac{P_0}{P_0-n*\sigma}    
\end{equation}
Equation \ref{eq:ILv3Stratbis} and its simplified version \ref{nasty_il} shows how nasty v3 impermanent loss can be for tighter bounds.\\
But one other very important thing has to be factored in : if we were to wait for a bound to be reached for rebalancing the position, we would then have to swap roughly half of our assets to enter a new position.\\
For huge AUM (asset under management) and fully on-chain rebalancing vaults, price slippages occurring during swaps can be very detrimental to the strategy.\\
AuM swapping costs are an essential part of the backtest : it will drive the optimal backtesting rebalancing parameters and will account for the asset under management scaling up : as AUM grows and swapping costs explodes, one will find optimal parameters with fewer rebalancing times.\\
We add a new parameter $\tau$, which is a number between 0 and 1. This parameter is intended to trigger a rebalancing each time we approach the upper or lower Bollinger band at a relative $\tau$ distance.\\
The trigger condition is defined by\\
\begin{equation}\label{trigger}
P \ge P_b-\tau P_b \text{ or } P \le P_a+\tau P_a  
\end{equation}
\subsection{Swapping costs}
The final asset quantities $X_f$ and $Y_f$ in the LP position can be found by using the final price $$P_f = P_b-\tau P_b \text{ or } P_f = P_a+\tau P_a $$ in equation \ref{three_regime}. Depending on whether we got triggered by the upper bound proximity or lower bound proximity, we will end up in a disequilibrium with the paroxysm reached for $\tau =0$ : then $P_f = P_b$ implicates that we are full in stable coins $Y$ and $P_f = P_a$ implicates that we are full in risky asset $X$.\\
We then have to swap part of either $X_f$ or $Y_f$ to fully reenter a position.\\

\section{Exhaustive optimization}
\subsection{Getting the optimal parameters: A trade-off between rebalancing costs, IL and generated fees}
The chosen bounds must also fit perfectly the price envelope for the optimal capital efficiency of your liquidity provisioning, while minimizing impermanent loss and swapping costs.\\
So in other words, we end up with the following constrained optimization problem :
\\
\begin{description}
  \item[$\bullet$]Maximize price inside the tightest bounds to earn volume fees (the tighter the bounds, the efficienter the capital)
  \item[$\bullet$] Impermanent loss and swapping slippage costs incurred at each rebalancing have to be minimized
\end{description}
We here propose an exhaustive search of the optimal parameters by running a backtest for each configuration and choosing the solution with the best Sharpe ratio.\\
\begin{equation}
\max_{(n, T, \tau, swap-costs)} \left[ Sharpe\left(n, T, \tau, swap-costs\right)\right]
\end{equation}
where $Sharpe\left(n, T, \tau, swap-costs\right)$ is the sharpe ratio of the backtested path.
\subsection{Simulating the fees generation}
We do use Dune Analytics to fetch the past volume $https://dune.com/queries/1343928$ and we use a rule of thumb volume pro rata to infer the past range APYs by just multiplying a snapshot of the APYs range by the pro rata of the current volume on the past one. This is a necessary approximation as we can't reproduce the whole past liquidity profile.\\

Find the average daily volume of a pool averaged over a week\\
Calculate the liquidity of a potential position for already fixed start and end points.\\
Calculate a distribution of the existing liquidity overlapping with each bucket.\\ This is similar to the views in both the flipside calculator and the liquidity view of the Uniswap analytics dashboard.\\
Use the normal distribution of the price pair (using one week of daily price movement to calculate volatility = standard deviation) to calculate the probability of the price being in each bucket. This of course makes the incorrect assumption that the past volatility will reflect the future, but hey, we gotta start somewhere. We can sum up all the buckets of the total start/end range to get an expected value for total 'liquidity coverage'.\\
Pulling everything together the calculation comes out to:\\

\begin{description}
  \item[$\bullet$ Daily Fees = Pool Volume * Pool Fee \% * Liquidity Coverage Expected Value]
  \item[$\bullet$ APY = (Daily Fees / 1000) * 365\\]
\end{description}
Finally choose the highest APY position for each pool

\subsection{Simulating the slippage}
We select the asset of minimal amount after the liquidity position triggered exit $\min\left( X_f*P_f, Y_f\right)$ and we swap the surplus $$\lvert X_f*P_f-Y_f \rvert$$ of $X_f$ or $Y_f$.\\
We choose to apply conservative swapping slippage costs as a map of the percentage size of AUM to swap. The map has been calibrated through as snapshot of the worst incurred slippage for a 1 million AUM for the chosen pair. \\
$$
swapping-cost-map=
$$
$$
\left\{1:10*1e-4,5:50*1e-4,10:0.01,
$$
$$
\left 50:0.05,75:0.07,100:0.08 \right\}
$$

\section{Results}\label{result}
We here present the optimal parameters for a 95 days backtest (largest historical volume period available for Orca).\\
The optimal parameters chosen are :
\left\{\begin{array}{lll}
T = 10\\
n = 3.5\\
\tau = 10.\\
\right.
\subsection{Absolute performance}
    \includegraphics[scale=0.2]{Plots/absolute_lp_perf.png}
    \caption{Absolute performance}
    \label{fig:conc_liquidity}
We here plot the absolute performance of the strategy against the stable coin. We have taken two approaches : one marking to market the LP value position according to the assets ratio, one just accounting for the LP value PnL at the rebalancing times. This allows to clearly demonstrate the impact of generated fees against cumulated rebalancing costs (impermanent loss, lp risky part depreciation and swapping costs).\\
We here remark that rebalancing P&L can be positive as we are in absolute performance, meaning that the LP risky asset appreciation has overtaken over impermanent loss and swap costs.
\subsection{Relative performance against 50/50 HODL basket}
    \includegraphics[scale=0.2]{Plots/hodl.png}
    \caption{Performance against a HODL basket}
    \label{fig:conc_liquidity}
We here plot the relative performance of the strategy against a 50/50 HODL basket. We have taken two approaches : one marking to market the LP value position according to the assets ratio, one just accounting for the LP value PnL at the rebalancing times. This allows to clearly demonstrate the impact of generated fees against cumulated rebalancing costs (impermanent loss and swapping costs).\\
We here remark that rebalancing P&L can only be negative as impermanent loss will lose on both risky asset price increase and decrease.
\subsection{Relative performance against risky asset}
    \includegraphics[scale=0.2]{Plots/risky.png}
    \caption{Performance against a full risky allocation}
    \label{fig:conc_liquidity}
We here plot the relative performance of the strategy against a full risky asset allocation. We have taken two approaches : one marking to market the LP value position according to the assets ratio, one just accounting for the LP value PnL at the rebalancing times. This allows to clearly demonstrate the impact of generated fees against cumulated rebalancing costs (impermanent loss and swapping costs).\\
This approach does favour the risky asset bear price move, as the LP position is buffering a part of it with cash, and therefore the good appreciation recently.\\
\subsection{Other variable}
\subsubsection{Algorithm optimal parameters}
We here display the Bollinger bands for the optimal parameters :
    \includegraphics[scale=0.2]{Plots/bollinger.png}
    \caption{Bollinger bands}
    \label{fig:conc_liquidity}
And the following derived bounds:
    \includegraphics[scale=0.2]{Plots/bounds_over_time.png}
    \caption{Liquidity bounds}
    \label{fig:conc_liquidity}
\subsubsection{Swapping costs}
The swapping costs losses computed at each rebalancing time:
    \includegraphics[scale=0.2]{Plots/swapping_cost.png}
    \caption{Swapping costs}
    \label{fig:conc_liquidity}
\subsubsection{Assets proportion over time}
We give also the assets proportion in the Liquidity position. Numeraire is the non risky stable asset. Here under is his evolution over time:
    \includegraphics[scale=0.2]{Plots/numeraire_over_time.png}
    \caption{Numeraire over time}
    \label{fig:conc_liquidity}
Risky asset over time:
    \includegraphics[scale=0.2]{Plots/risky_over_time.png}
    \caption{Risky asset over time}
    \label{fig:conc_liquidity}
\subsubsection{Sensitivity analysis}
We here give financial standard kpis around the optimal parameters.\\\\
